Modeling Intervention Strategies for United States TB Control

### 2014-03-02 in_progress/presentations/paper/draft.tex
modified draft.tex to remove formatting weirdness
added results plan
spelling correction
added Background on TB

{\huge \color{red} List of results}
\begin{itemize}
  \item Plateauing Effect
  \item Intervention Analysis
  \item Statistical Analysis of Hill Model
  \item Agent-Based Feasibility
  \item Theoretical/Experimental justification of basic reproduction number
  \item Overall qualitative strategy conclusions. 
\end{itemize}<++>

@@

\section{Background}
\subsection{Tuberculosis}
{\huge \color{red} Add background info about TB. Latent phase, etc. I think it
makes sense to give it its own section. COLIN}
\subsection{The Hill Model}
A flowchart representation of the Hill Model is shown in
Figure~\ref{fig:hillModelSchematic}. Each compartment represents a different
possible health state with respect to TB for every US-born or foreign-born
individual, and arrows between different compartments represent possible
transitions between states.  Individuals also leave the model from all
compartments due to natural death, which is left out of the figure for clarity.

>>>>

{\huge \color{red} List of results}
Plan:
\begin{enumerate}
  \item Intervention Analysis: 
    \begin{enumerate}
      \item Reducing Entering LTBI
      \item Cutting Transmission
      \item Reducing Progression Rate
    \end{enumerate}
  \item Qualitative Strategy Conclusions:
    \begin{enumerate}
      \item Sourced Incidence \& Cost
      \item Plateauing Effect
      \item Extremal values for entering LTBI reduction
      \item Linearity in Cost/Incidence for entering LTBI reduction
      \item CPCA data
    \end{enumerate}
  \item Statistical Verification/Agent Based Feasibility
    \begin{enumerate}
      \item Normal Distributions
      \item Basic Reproductive Numbers
      \item Agetn based running time \& Extensibility. 
    \end{enumerate}
\end{enumerate}
Ideas:
\begin{itemize}
  \item Plateauing Effect
  \item Intervention Analysis
  \item Statistical Analysis of Hill Model
  \item Agent-Based Feasibility
  \item Theoretical/Experimental justification of basic reproduction number
  \item Overall qualitative strategy conclusions. 
\end{itemize}

@@

\section{Background}
\subsection{Tuberculosis}
Tuberculosis is an infectious bacterial disease that primarily affects the lungs,
with common symptoms including severe coughing, fevers, and chest pain.
Tuberculosis is a major global health concern, the World Health Organization
 estimates that 8.6 million developed TB and and 1.3 million people died from
 the disease in 2012.  As an airborne disease, \emph{Mycobacterium tuberculosis}
 is typically transmitted from person-to-person by coughing, sneezing, and the 
exchange of other respiratory fluids.  Infected individuals first enter a latent phase,
 during which \emph{Mycobacterium tuberculosis} is present in their bodies,
but the individuals remain asymptomatic and noncontagious. 
The lifetime risk of progressing from Latent TB Infection (LTBI) to Active TB is approximately
5-10\%, although individuals with LTBI have the greatest chance of developing 
Active TB during the first two years immediately following infection. 
Cases of Active TB may be classified as pulmonary (~80\% of cases) or 
non-pulmonary (~20\% of cases), depending upon the biological location of infection.
In the Hill model, pulmonary Active TB is treated as contagious and non-pulmonary 
Active TB is treated as  non-contagious, which is an assumption we also use here.  \\

In the United States, 9,951 new cases of TB were reported in 2012 by the Centers for Disease
Control. The disease burden varied for different subpopulations in the U.S., and in particular
the incidence rate of TB was 11.5 times higher for the foreign-born (FB) population
than the US-born (USB) population.  For the past 20 years, the overall incidence of
TB in the U.S. has declined each year, but in 2012 the annual incidence level of 32 new cases/million
remains above the desired goal of the $<$1 new case/million, which is the target
for disease elimination set by the Centers for Disease Control. \\

citations: CDC Tuberuclosis 2013 Report - http://www.cdc.gov/mmwr/preview/mmwrhtml/mm6211a2.htm
WHO Global Tuberculosis Report 2013 - http://www.who.int/tb/publications/global\_report/en/ \\

\subsection{The Hill Model}
A flowchart representation of the Hill Model is shown in
Figure~\ref{fig:hillModelSchematic}. Each compartment represents a different
possible health state with respect to TB for every US-born or foreign-born
individual, and arrows between different compartments represent possible
transitions between states.  Individuals also leave the model from all
compartments due to natural death, which is left out of the figure for clarity.
